---
title: "MAP & Mindprint"
author: "Felicia Zhang"
date: '2018-12-07'
output: pdf_document
toc: yes
toc_depth: 2
fontsize: 12pt
fig_height: 6
fig_width: 7

---

```{r setup, include=FALSE, warning=FALSE}
## LOAD PACKAGES

library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)
library(readxl)    
library(extrafont)
library(glmnet)
library(GGally)
library(readxl)
library(corrplot)
library(GGally)
library(rpart)
library(rpart.plot)
library(partykit)
library(knitr)

## LOAD MAP DATA

# Load multiple excel sheets at once

# get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/MAPdata/Elm Place MAP Scores.xlsx")

# load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/MAPdata/Elm Place MAP Scores.xlsx", sheet = sheet)
)

# prepare names
names(lst) <- sheets

# turn each sheet into DF
list2env(lst, envir = .GlobalEnv)

## LOAD MINDPRINT DATA

MindprintDF <- read_xlsx("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/MAPdata/Mindprint Student Data.xlsx")

# Mindprint scores are from grade 7 students. MAP scores are from grade 6 and grade 8 students. 
``` 

```{r, include=FALSE, warning=FALSE}
# for Mindprint _SCORE columns, figure out which rows contain "error_error"
a <- c(which(MindprintDF$SM_SCORE=="error_error"), which(MindprintDF$VMEM_SCORE=="error_error"), which(MindprintDF$ABF_SCORE=="error_error"), which(MindprintDF$LAN_SCORE=="error_error"), which(MindprintDF$NVR_SCORE=="error_error"), which(MindprintDF$WM_SCORE=="error_error"), which(MindprintDF$ATT_SCORE=="error_error"), which(MindprintDF$SMEM_SCORE=="error_error"), which(MindprintDF$SPA_SCORE=="error_error"))

aa <- unique(a)

# remove rows that say "_error" 
MindprintDF <- MindprintDF[-aa,]

# remove students who didn't try on mindprint: 2256, 2313, 2220, 2234, 2263, 2207
MindprintDF <- subset(MindprintDF, customer_id != 2256 & customer_id != 2313 & customer_id != 2220 & customer_id != 2234 & customer_id != 2263 & customer_id != 2207)
```

```{r, include=FALSE, warning=FALSE}
## Combine Mindprint and MAP scores

# remove irrelevant MAP columns

MAP <- Sheet1
MAP$TestType <- NULL
MAP$TestName <- NULL
MAP$TestStartDate <- NULL

names(MAP)[1] <- "customer_id"

# combine
finalDF <- merge(MindprintDF,MAP,by="customer_id")
finalDF$category <- paste(finalDF$Grade, finalDF$Discipline)

# for MAP scores, remove students that didn't take all the tests for both years
subs <- unique(finalDF$customer_id)
removesub <- vector()

for (i in 1:length(subs)) {
  a <- length(which(finalDF$customer_id==subs[i]))
  if (a!=5) {
  removesub <- c(removesub, subs[i])
  }
}

b <- c(which(finalDF$customer_id==2209), which(finalDF$customer_id==2257), which(finalDF$customer_id==2277), which(finalDF$customer_id==2285), which(finalDF$customer_id==2302))

finalDF <- finalDF[-b,]

write.csv(finalDF, "MAP_MP.csv", row.names=TRUE) #save to computer
``` 

## Distribution of MAP Percentiles
```{r, echo=FALSE, warning=FALSE, fig.align='center'}

ggplot(finalDF, aes(x=TestPercentile, fill=factor(Grade)))+
  geom_histogram(binwidth=5)+
  theme_bw()+
  theme(panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Percentile", y = "Number of students")+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_wrap(~Discipline)+
  theme_bw(base_family = "Times", base_size=14)+
  theme(legend.position = "top")+  
  scale_y_continuous(limits=c(0,40),breaks=seq(0,40,5))+
  scale_fill_brewer(palette="Set1",name="Grade")

```

## Distribution of MAP RIT Score
```{r, echo=FALSE, warning=FALSE, fig.align='center'}
ggplot(finalDF, aes(x=TestRITScore, fill=factor(Grade)))+
  geom_histogram(binwidth=5)+
  theme_bw()+
  theme(panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "RIT Score", y = "Number of students")+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_wrap(~Discipline)+
  theme_bw(base_family = "Times", base_size=14)+
  theme(legend.position = "top")+
  scale_y_continuous(limits=c(0,40),breaks=seq(0,40,5))+
  scale_fill_brewer(palette="Set1",name="Grade")

```

## Distribution of MAP Test Duration
```{r, echo=FALSE, warning=FALSE, fig.align='center'}
ggplot(finalDF, aes(x=TestDurationMinutes, fill=factor(Grade)))+
  geom_histogram(binwidth=5)+
  theme_bw()+
  theme(panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Test duration (minutes)", y = "Number of students")+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_wrap(~Discipline)+
  theme_bw(base_family = "Times", base_size=14)+
  theme(legend.position = "top")+
  scale_y_continuous(limits=c(0,20),breaks=seq(0,20,5))+
  scale_fill_brewer(palette="Set1",name="Grade")

```
\newpage

## Correlations between overall RIT score, percentile and test duration
```{r, echo=FALSE, warning=FALSE}
# grouped all the subjects and grades together

# correlation matrix
foo <- finalDF[,46:50]
foo$TestStandardError <- NULL

# plot
ggcorr(foo, palette = "RdBu", label = TRUE, label_size = 7)
```
\newpage

## Correlations between RIT scores
```{r, echo=FALSE, warning=FALSE}
# separated by subject and grade

# correlation matrix
foo <- finalDF[,c(1,46:50)]

# using RIT score
foo <- foo[,c(1,3,6)]

# change from long to wide
foo_wide <- spread(foo, category, TestRITScore)

foo2 <- reshape(foo, idvar = "customer_id", timevar = "category", direction = "wide")
foo2$customer_id <- NULL

# rename columns
names(foo2)[1] <- "Gr8_Reading"
names(foo2)[2] <- "Gr8_Math"
names(foo2)[3] <- "Gr6_Math"
names(foo2)[4] <- "Gr6_Reading"
names(foo2)[5] <- "Gr6_Science"

# plot
ggcorr(foo2, label = TRUE, label_size = 7)
```

## Correlations between percentiles
```{r, echo=FALSE, warning=FALSE}
# separated by subject and grade

# correlation matrix
foo <- finalDF[,c(1,46:50)]

# using percentile 
foo <- foo[,c(1,5,6)]

# change from long to wide
foo_wide <- spread(foo, category, TestPercentile)

foo2 <- reshape(foo, idvar = "customer_id", timevar = "category", direction = "wide")
foo2$customer_id <- NULL

# rename columns
names(foo2)[1] <- "Gr8_Reading"
names(foo2)[2] <- "Gr8_Math"
names(foo2)[3] <- "Gr6_Math"
names(foo2)[4] <- "Gr6_Reading"
names(foo2)[5] <- "Gr6_Science"

# plot
ggcorr(foo2, label = TRUE, label_size = 7)
```

\newpage

```{r, echo=FALSE, warning=FALSE}
# remove not useful mindprint features
drops <- c("gender","customer_id","SM_SCORE","VMEM_SCORE","ABF_SCORE","LAN_SCORE","NVR_SCORE","WM_SCORE","ATT_SCORE", "SMEM_SCORE", "SPA_SCORE")
features <- finalDF[ , !(names(finalDF) %in% drops)]
outcomes <- features[,c(36:39)]
features <- features[,-c(27:34,36,37,38)]
```

# Tree models

## Grade 6 Reading trees - percentile
```{r, echo=FALSE, warning=FALSE, fig.height=6.1}
x <- subset(features, category == "6 Reading")
x$category <- NULL

y <- outcomes$TestPercentile[outcomes$category=="6 Reading"]

# combine 
loo <- cbind(x, y)

# 1. grow tree 
tree <- rpart(y~., method="anova", minsplit=20, minbucket=20, maxdepth=3, data=loo)
# 
# printcp(tree) # display the results 
# plotcp(tree) # visualize cross-validation results 
# 
# # 2. find best cp
# bestcp <- tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
# 
# # 3. Prune the tree using the best cp.
# tree.pruned <- prune(tree, cp = bestcp)

# Plot
plot(as.party(tree))
#box plots of the outcome that we are trying to predict.

# calculate SD and mean
stats <- aggregate(loo$y, list(tree$where), sd)
names(stats)[1] <- "node"
names(stats)[2] <- "sd"
stats2 <- aggregate(loo$y, list(tree$where), mean)
names(stats2)[2] <- "mean"
stats$mean <- stats2$mean

kable(stats, format = "markdown", align = 'c', row.names=F)
```

Verbal reasoning accuracy and efficiency are important for Grade 6 reading.

## Grade 6 Math trees - percentile
```{r, echo=FALSE, warning=FALSE, fig.height=6.1}
x <- subset(features, category == "6 Mathematics")
x$category <- NULL

y <- outcomes$TestPercentile[outcomes$category=="6 Mathematics"]

# combine 
loo <- cbind(x, y)

# 1. grow tree 
tree <- rpart(y~., method="anova", minsplit=20, minbucket=20, maxdepth=3, data=loo)
# 
# printcp(tree) # display the results 
# plotcp(tree) # visualize cross-validation results 
# 
# # 2. find best cp
# bestcp <- tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
# 
# # 3. Prune the tree using the best cp.
# tree.pruned <- prune(tree, cp = bestcp)

# Plot
plot(as.party(tree))
#box plots of the outcome that we are trying to predict.

# calculate SD and mean
stats <- aggregate(loo$y, list(tree$where), sd)
names(stats)[1] <- "node"
names(stats)[2] <- "sd"
stats2 <- aggregate(loo$y, list(tree$where), mean)
names(stats2)[2] <- "mean"
stats$mean <- stats2$mean

kable(stats, format = "markdown", align = 'c', row.names=F)
```

Test duration, verbal reasoning efficiency and abstract reasoning accuracy are important for Grade 6 math.

## Grade 6 Science trees - percentile
```{r, echo=FALSE, warning=FALSE, fig.height=6.1}
x <- subset(features, category == "6 Science")
x$category <- NULL

y <- outcomes$TestPercentile[outcomes$category=="6 Science"]

# combine 
loo <- cbind(x, y)

# 1. grow tree 
tree <- rpart(y~., method="anova", minsplit=20, minbucket=20, maxdepth=3, data=loo)

# printcp(tree) # display the results 
# plotcp(tree) # visualize cross-validation results 
# 
# # 2. find best cp
# bestcp <- tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
# 
# # 3. Prune the tree using the best cp.
# tree.pruned <- prune(tree, cp = bestcp)

# Plot
plot(as.party(tree))
#box plots of the outcome that we are trying to predict.

# calculate SD and mean
stats <- aggregate(loo$y, list(tree$where), sd)
names(stats)[1] <- "node"
names(stats)[2] <- "sd"
stats2 <- aggregate(loo$y, list(tree$where), mean)
names(stats2)[2] <- "mean"
stats$mean <- stats2$mean

kable(stats, format = "markdown", align = 'c', row.names=F)
```

Verbal reasoning accuracy and verbal memory accuracy are important for Grade 6 science.

## Grade 8 Reading trees - percentile
```{r, echo=FALSE, warning=FALSE, fig.height=6.1}
x <- subset(features, category == "8 Reading")
x$category <- NULL

y <- outcomes$TestPercentile[outcomes$category=="8 Reading"]

# combine 
loo <- cbind(x, y)

# 1. grow tree 
tree <- rpart(y~., method="anova", minsplit=20, minbucket=20, maxdepth=2, data=loo)
# 
# printcp(tree) # display the results 
# plotcp(tree) # visualize cross-validation results 
# 
# # 2. find best cp
# bestcp <- tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
# 
# # 3. Prune the tree using the best cp.
# tree.pruned <- prune(tree, cp = bestcp)

# Plot
plot(as.party(tree))
#box plots of the outcome that we are trying to predict.

# calculate SD and mean
stats <- aggregate(loo$y, list(tree$where), sd)
names(stats)[1] <- "node"
names(stats)[2] <- "sd"
stats2 <- aggregate(loo$y, list(tree$where), mean)
names(stats2)[2] <- "mean"
stats$mean <- stats2$mean

kable(stats, format = "markdown", align = 'c', row.names=F)
```

Verbal reasoning accuracy is important for Grade 8 reading.

## Grade 8 Math trees - percentile
```{r, echo=FALSE, warning=FALSE, fig.height=6.1}
x <- subset(features, category == "8 Mathematics")
x$category <- NULL

y <- outcomes$TestPercentile[outcomes$category=="8 Mathematics"]

# combine 
loo <- cbind(x, y)

# 1. grow tree 
tree <- rpart(y~., method="anova", minsplit=20, minbucket=20, maxdepth=3, data=loo)
# 
# printcp(tree) # display the results 
# plotcp(tree) # visualize cross-validation results 
# 
# # 2. find best cp
# bestcp <- tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
# 
# # 3. Prune the tree using the best cp.
# tree.pruned <- prune(tree, cp = bestcp)

# Plot
plot(as.party(tree))
#box plots of the outcome that we are trying to predict.

# calculate SD and mean
stats <- aggregate(loo$y, list(tree$where), sd)
names(stats)[1] <- "node"
names(stats)[2] <- "sd"
stats2 <- aggregate(loo$y, list(tree$where), mean)
names(stats2)[2] <- "mean"
stats$mean <- stats2$mean

kable(stats, format = "markdown", align = 'c', row.names=F)
```

Verbal reasoning efficiency and abstract reasoning accuracy are important for Grade 8 math.

\newpage

## Comparing RIT and percentile regression trees
```{r, echo=FALSE, warning=FALSE, fig.align='center'}
# kable
treesummary <- data.frame( "Grade" = integer(10), "Subject" = character(10),"Outcome" = character(10), "Level1" = character(10), "Level2" = character(10), "Level3" = character(10))

a <- c(6,6,6,8,8,6,6,6,8,8)
b <- c("Reading","Math","Science","Reading","Math","Reading","Math","Science","Reading","Math")
c <- c("RIT","RIT","RIT","RIT","RIT","Percentile","Percentile","Percentile","Percentile","Percentile")
d <- c("LAN_Az","TestDuration","LAN_Az","LAN_Az","LAN_Az","LAN_Az","TestDuration","LAN_Az","LAN_Az","LAN_eff")
e <- c("LAN_eff","LAN_eff","VMEM_eff","LAN_Az","TestDuration","LAN_eff","LAN_eff","VMEM_Az","LAN_Az","NVR_Az")
f <- c(NA,"NVR_Az","ABF_Az",NA,NA,NA,"NVR_Az",NA,NA,NA)

treesummary$Grade <- a
treesummary$Subject <- b
treesummary$Outcome <- c
treesummary$Level1 <- d
treesummary$Level2 <- e
treesummary$Level3 <- f

kable(treesummary, format = "markdown", align = 'c', row.names=F, caption = 'Comparison of RIT and percentile')
```
The biggest difference is between Grade 8 Math RIT and Grade 8 Math percentile

## Comparing grade 6 and grade 8 regression trees (percentile)
```{r, echo=FALSE, warning=FALSE, fig.align='center'}
# kable
treesummary <- data.frame( "Grade" = integer(4), "Subject" = character(4),"Outcome" = character(4), "Level1" = character(4), "Level2" = character(4), "Level3" = character(4))

a <- c(6,8,6,8)
b <- c("Reading","Reading","Math","Math")
c <- c("Percentile","Percentile","Percentile","Percentile")
d <- c("LAN_Az","LAN_Az","TestDuration","LAN_eff")
e <- c("LAN_eff","LAN_Az","LAN_eff","NVR_Az")
f <- c(NA,NA,"NVR_Az",NA)

treesummary$Grade <- a
treesummary$Subject <- b
treesummary$Outcome <- c
treesummary$Level1 <- d
treesummary$Level2 <- e
treesummary$Level3 <- f

kable(treesummary, format = "markdown", align = 'c', row.names=F)
```

## Comparing grade 6 and grade 8 regression trees (RIT score)
```{r, echo=FALSE, warning=FALSE, fig.align='center'}
# kable
treesummary <- data.frame( "Grade" = integer(4), "Subject" = character(4),"Outcome" = character(4), "Level1" = character(4), "Level2" = character(4), "Level3" = character(4))

a <- c(6,8,6,8)
b <- c("Reading","Reading","Math","Math")
c <- c("RIT","RIT","RIT","RIT")
d <- c("LAN_Az","LAN_Az","TestDuration","LAN_Az")
e <- c("LAN_eff","LAN_Az","LAN_eff","TestDuration")
f <- c(NA,NA,"NVR_Az",NA)

treesummary$Grade <- a
treesummary$Subject <- b
treesummary$Outcome <- c
treesummary$Level1 <- d
treesummary$Level2 <- e
treesummary$Level3 <- f

kable(treesummary, format = "markdown", align = 'c', row.names=F)
```

```{r, echo=FALSE, warning=FALSE, fig.align='center'}

``` 



