---
title: "Mindprint"
author: "Felicia Zhang"
date: '2018-07-25'
output: pdf_document
toc: yes
toc_depth: 2
fontsize: 12pt
fig_height: 5
fig_width: 7
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, warning=FALSE}
## LOAD PACKAGES

library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)
library(readxl)    
library(extrafont)
library(glmnet)
library(GGally)
library(readxl)
library(corrplot)
```

```{r setup, include=FALSE, warning=FALSE}
## LOAD ACT DATA

# Load multiple excel sheets at once

# get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/ACTData_112418.xlsx")

# load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/ACTData_112418.xlsx", sheet = sheet)
)

# prepare names
names(lst) <- sheets

# turn each sheet into DF
list2env(lst, envir = .GlobalEnv)

# the one called the Combo is a mixture of SAT and ACT questions.
# 0 = incorrect, 1 = correct, 2 = skip

# 9 versions of test: 70A, 70C, 70G, 71A, 71C, 71E, 72C, 72E, Combo
# 4 subjects: English, Math, Reading, Science
```

```{r setup, include=FALSE, warning=FALSE}
## LOAD MINDPRINT DATA

MindprintDF <- read_xlsx("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/MindprintData_112418.xlsx")

## LOAD CONVERT RAW DATA TO SCALED DATA TABLES

# Load multiple excel sheets at once

# get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/ConvertRawToScaledScores.xlsx")

# load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/ConvertRawToScaledScores.xlsx", sheet = sheet)
)

# prepare names
names(lst) <- sheets

# turn each sheet into DF
list2env(lst, envir = .GlobalEnv)

#difference between 70C, 72C, Combo v2.4: three different tests based on where we had sufficient student data, noting the one called the Combo is a mixture of SAT and ACT questions.
```

Hypotheses of which skills are key drivers by ACT subject test

a.	English – Primary would be Verbal Reasoning
i.	Usage Mechanics (UM) (grammar and punctuation): Verbal Reasoning and/or Verbal Memory and Visual Memory
ii.	Rhetorical analysis (RH): Verbal Reasoning and Abstract Reasoning

b.	Math – Primary would be abstract reasoning
i.	Algebra: Abstract Reasoning, Visual Memory and maybe Verbal Reasoning
ii.	Geometry: Abstract Reasoning, Visual Memory, Spatial Perception
iii.Advanced Algebra and Geometry: Abstract Reasoning, Spatial Perception and Flexible Thinking

c.	Reading – Primary would be verbal reasoning but maybe working memory
i.	Natural sciences: Verbal Reasoning and Abstract Reasoning
ii.	Others: Verbal Reasoning and Flexible Thinking for the hardest questions/inferencing

d.	Science – Could be all three reasoning: Verbal, Abstract and Spatial
i.	Interpreting Graphs, Figures & Tables: Abstract and Spatial

```{r setup, include=FALSE, warning=FALSE}
# For each ACT version, count number of questions for each section
# 70A, 70C, 70G, 71A, 71C, 71E, 72C, 72E, 72F, 72G, 73E, 74F, 74H, Combo 

length(which(ACT70A[2,]=="English")) #75
length(which(ACT70A[2,]=="Math")) #60 
length(which(ACT70A[2,]=="Reading")) #40
length(which(ACT70A[2,]=="Science")) #40

length(which(ACT70C[3,]=="English")) #75
length(which(ACT70C[3,]=="Math")) #60
length(which(ACT70C[3,]=="Reading")) #40
length(which(ACT70C[3,]=="Science")) #40

length(which(ACT70G[3,]=="English")) #75
length(which(ACT70G[3,]=="Math")) #60
length(which(ACT70G[3,]=="Reading")) #40
length(which(ACT70G[3,]=="Science")) #40

length(which(ACT71A[2,]=="English")) #75
length(which(ACT71A[2,]=="Math")) #60
length(which(ACT71A[2,]=="Reading")) #40
length(which(ACT71A[2,]=="Science")) #40

length(which(ACT71C[2,]=="English")) #75
length(which(ACT71C[2,]=="Math")) #60
length(which(ACT71C[2,]=="Reading")) #40
length(which(ACT71C[2,]=="Science")) #40

length(which(ACT71E[2,]=="English")) #75
length(which(ACT71E[2,]=="Math")) #60
length(which(ACT71E[2,]=="Reading")) #40
length(which(ACT71E[2,]=="Science")) #40

length(which(ACT72C[3,]=="English")) #75
length(which(ACT72C[3,]=="Math")) #60
length(which(ACT72C[3,]=="Reading")) #40
length(which(ACT72C[3,]=="Science")) #40

length(which(ACT72E[3,]=="English")) #75
length(which(ACT72E[3,]=="Math")) #60
length(which(ACT72E[3,]=="Reading")) #40
length(which(ACT72E[3,]=="Science")) #40

length(which(ACT74F[2,]=="English")) #75
length(which(ACT74F[2,]=="Math")) #60
length(which(ACT74F[2,]=="Reading")) #40
length(which(ACT74F[2,]=="Science")) #40

# For Combo test calculate standard score using both ACT and SAT test
length(which(ACTCombo2.4[3,]=="English")) #39
length(which(ACTCombo2.4[3,]=="Math")) #61
length(which(ACTCombo2.4[3,]=="Reading")) #50
length(which(ACTCombo2.4[3,]=="Science")) #24
length(which(ACTCombo2.4[3,]=="Writing")) #22

# How many questions for each subsection...each test has different number of questions and topics for subsection...
# length(which(ACT72C[3,]=="English" & ACT72C[4,]=="UM")) #51
# length(which(ACT72C[3,]=="English" & ACT72C[4,]=="RH")) #24
# length(which(ACT72C[3,]=="Math" & ACT72C[4,]=="Pre-Algebra")) #24
# length(which(ACT72C[3,]=="Math" & ACT72C[4,]=="Plane Geometry/Trigonometry")) #18
# length(which(ACT72C[3,]=="Math" & ACT72C[4,]=="Interm Alg/Cood Geometry")) #18
# length(which(ACT72C[3,]=="Reading" & ACT72C[4,]=="Art/Literature")) #20
# length(which(ACT72C[3,]=="Reading" & ACT72C[4,]=="Social Studies/Sciences")) #20
# 
# length(which(ACT71C[2,]=="English" & ACT71C[3,]=="UM")) #55
# length(which(ACT71C[2,]=="English" & ACT71C[3,]=="RH")) #20
# length(which(ACT71C[2,]=="Math" & ACT71C[3,]=="EA")) #19
# length(which(ACT71C[2,]=="Math" & ACT71C[3,]=="GT")) #20
# length(which(ACT71C[2,]=="Math" & ACT71C[3,]=="AG")) #21
# length(which(ACT71C[2,]=="Reading" & ACT71C[3,]=="Humanities")) #10
# length(which(ACT71C[2,]=="Reading" & ACT71C[3,]=="Natural Science")) #10
# length(which(ACT71C[2,]=="Reading" & ACT71C[3,]=="Prose")) #10
# length(which(ACT71C[2,]=="Reading" & ACT71C[3,]=="Social Science")) #10
```

```{r setup, include=FALSE, warning=FALSE}
# Combine these DFs: 70C, 70G, 71A, 71C, 71E, 72C, 72E, 72F, 72G, 73E, 74F, 74H, Combo 
# 
# # Combine test information together
# # 70C
# foo <- ACT70C[1:5,]
# foo[1,] <- "70C"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# ACTinfo <- foo[-1, ]
# 
# # 70G
# foo <- ACT70G[1:5,]
# foo[1,] <- "70G"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 71A
# foo <- ACT71A[1:4,]
# newrow <- foo[1,]
# foo <- rbind(newrow,foo)
# foo[1,] <- "71A"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 71C
# foo <- ACT71C[1:4,]
# newrow <- foo[1,]
# foo <- rbind(newrow,foo)
# foo[1,] <- "71C"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 71E
# foo <- ACT71E[1:4,]
# newrow <- foo[1,]
# foo <- rbind(newrow,foo)
# foo[1,] <- "71E"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 72C
# foo <- ACT72C[1:5,]
# foo[1,] <- "72C"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 72E
# foo <- ACT72E[1:5,]
# foo[1,] <- "72E"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # 74F
# foo <- ACT74F[1:4,]
# newrow <- foo[1,]
# foo <- rbind(newrow,foo)
# foo[1,] <- "74F"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # Combo
# foo <- ACTCombo2.4[1:5,]
# foo[1,] <- "Combo"
# foo[1,1] <- "Test"
# foo[2,1] <- "Test_Question"
# foo[3,1] <- "Test_Section"
# foo[4,1] <- "Test_Subsection"
# foo[5,1] <- "Difficulty"
# foo <- transpose(foo)
# colnames(foo) <- foo[1, ]
# foo <- foo[-1, ]
# ACTinfo <- rbind(ACTinfo, foo)
# 
# # Convert to numeric
# ACTinfo$Test_Question <- as.numeric(as.character(ACTinfo$Test_Question))
# ACTinfo$Difficulty <- as.numeric(as.character(ACTinfo$Difficulty))
# 
# # Add in TestQuestion2 which is 1:215
# ACTinfo$Test_Question2 <- 0
# ACTinfo$Test_Question2[1:1720] <- rep(1:215, times=8)
# # Add in TestQuestion2 separately for combo since they don't have the same number of questions
# ACTinfo$Test_Question2[1721:length(ACTinfo$Test_Question)] <- 1:length(foo$Test)
```

## Convert ACT raw scores to scaled scores
### Version: 70C
```{r setup, include=FALSE, warning=FALSE}
# Get raw scores
foo <- ACT70C[-c(1:7), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "70C"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `70C`$English_Scaled_Score[`70C`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `70C`$Math_Scaled_Score[`70C`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `70C`$Reading_Scaled_Score[`70C`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `70C`$Science_Scaled_Score[`70C`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- foo
```

### Version: 70G
```{r}
# Get raw scores
foo <- ACT70G[-c(1:6), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "70G"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `70G`$English_Scaled_Score[`70G`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `70G`$Math_Scaled_Score[`70G`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `70G`$Reading_Scaled_Score[`70G`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `70G`$Science_Scaled_Score[`70G`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 71A
```{r}
# Get raw scores
foo <- ACT71A[-c(1:5), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "71A"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `71A`$English_Scaled_Score[`71A`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `71A`$Math_Scaled_Score[`71A`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `71A`$Reading_Scaled_Score[`71A`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `71A`$Science_Scaled_Score[`71A`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 71C
```{r}
# Get raw scores
foo <- ACT71C[-c(1:5), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "71C"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `71C`$English_Scaled_Score[`71C`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `71C`$Math_Scaled_Score[`71C`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `71C`$Reading_Scaled_Score[`71C`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `71C`$Science_Scaled_Score[`71C`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 71E
``` {r}
# Get raw scores
foo <- ACT71E[-c(1:5), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "71E"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `71E`$English_Scaled_Score[`71E`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `71E`$Math_Scaled_Score[`71E`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `71E`$Reading_Scaled_Score[`71E`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `71E`$Science_Scaled_Score[`71E`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 72C
```{r}
# Get raw scores
foo <- ACT72C[-c(1:6), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "72C"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `72C`$English_Scaled_Score[`72C`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `72C`$Math_Scaled_Score[`72C`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `72C`$Reading_Scaled_Score[`72C`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `72C`$Science_Scaled_Score[`72C`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 72E
```{r}
# Get raw scores
foo <- ACT72E[-c(1:6), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "72E"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `72E`$English_Scaled_Score[`72E`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `72E`$Math_Scaled_Score[`72E`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `72E`$Reading_Scaled_Score[`72E`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `72E`$Science_Scaled_Score[`72E`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 72F
```{r}
# Get raw scores
foo <- ACT72F[-c(1:4), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "72F"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `72F`$English_Scaled_Score[`72F`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `72F`$Math_Scaled_Score[`72F`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `72F`$Reading_Scaled_Score[`72F`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `72F`$Science_Scaled_Score[`72F`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 72G
```{r}
# Get raw scores
foo <- ACT72G[-c(1:4), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "72G"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `72G`$English_Scaled_Score[`72G`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `72G`$Math_Scaled_Score[`72G`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `72G`$Reading_Scaled_Score[`72G`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `72G`$Science_Scaled_Score[`72G`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 73E
```{r}
# Get raw scores
foo <- ACT73E[-c(1:4), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "73E"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `73E`$English_Scaled_Score[`73E`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `73E`$Math_Scaled_Score[`73E`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `73E`$Reading_Scaled_Score[`73E`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `73E`$Science_Scaled_Score[`73E`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: 74F
```{r}
# Get raw scores
foo <- ACT74F[-c(1:5), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "74F"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `74F`$English_Scaled_Score[`74F`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `74F`$Math_Scaled_Score[`74F`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `74F`$Reading_Scaled_Score[`74F`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `74F`$Science_Scaled_Score[`74F`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)

```

### Version: 74H
```{r}
# Get raw scores
foo <- ACT74H[-c(1:4), ]
colnames(foo) <- c(1,1:215)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "74H"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- rowSums(foo[,2:76], na.rm = TRUE)
foo$MathRaw <- rowSums(foo[,77:136], na.rm = TRUE)
foo$ReadingRaw <- rowSums(foo[,137:176], na.rm = TRUE)
foo$ScienceRaw <- rowSums(foo[,177:216], na.rm = TRUE)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:216)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- `74H`$English_Scaled_Score[`74H`$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- `74H`$Math_Scaled_Score[`74H`$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- `74H`$Reading_Scaled_Score[`74H`$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- `74H`$Science_Scaled_Score[`74H`$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)
```

### Version: ACTCombo
```{r}
# Get raw scores
foo <- ACTCombo2.4[-c(1:6), ]
colnames(foo) <- c(1,1:196)
colnames(foo)[1] <- "customer_id"
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
foo$ACTversion <- "Combo"

# replace skipped questions with NA
foo[foo==2] <- NA

foo$EngRaw <- round(rowSums(foo[,2:40], na.rm = TRUE) / 39 * 100, digits = 0)
foo$ReadingRaw <- round(rowSums(foo[,c(41:70,123:142)], na.rm = TRUE) / 50 * 100, digits = 0)
foo$MathRaw <- round(rowSums(foo[,c(71:100,143:173)], na.rm = TRUE) / 61 * 100, digits = 0)
foo$ScienceRaw <- round(rowSums(foo[,174:197], na.rm = TRUE) / 24 * 100, digits = 0)

# replace 0 with NA
foo$EngRaw[foo$EngRaw==0] <- NA
foo$MathRaw[foo$MathRaw==0] <- NA
foo$ReadingRaw[foo$ReadingRaw==0] <- NA
foo$ScienceRaw[foo$ScienceRaw==0] <- NA

# remove columns
foo <- foo[,-(2:197)]

# create columns
foo$EngScaledScore <- 0
foo$MathScaledScore <- 0
foo$ReadingScaledScore <- 0
foo$ScienceScaledScore <- 0

# convert English scores
for (i in 1:length(foo$customer_id)){
  foo$EngScaledScore[i] <- Combo$English_Scaled_Score[Combo$English_Raw_Score==foo$EngRaw[i]]
}

# convert Math scores
for (i in 1:length(foo$customer_id)){
  foo$MathScaledScore[i] <- Combo$Math_Scaled_Score[Combo$Math_Raw_Score==foo$MathRaw[i]]
}

# convert Reading scores
for (i in 1:length(foo$customer_id)){
  foo$ReadingScaledScore[i] <- Combo$Reading_Scaled_Score[Combo$Reading_Raw_Score==foo$ReadingRaw[i]]
}

# convert Science scores
for (i in 1:length(foo$customer_id)){
  foo$ScienceScaledScore[i] <- Combo$Science_Scaled_Score[Combo$Science_Raw_Score==foo$ScienceRaw[i]]
}

ACTscaledscores <- rbind(ACTscaledscores, foo)

## Merge with Mindprint DF
MindprintDF_yescombo <- merge(MindprintDF, ACTscaledscores, by = "customer_id")

# save to computer
write.csv(MindprintDF_yescombo, "Mindprint_ScaledScores_YesCombo.csv", row.names=TRUE) #save to computer
```

Identify missing data
```{r}
# Identify students who are missing Mindprint scores
for (i in 1:length(ACTscaledscores$customer_id)) {
  # we have their ACT scores
  z <- ACTscaledscores$customer_id[i]
  zz <- which(MindprintDF$customer_id==z)
  # but not their mindprint scores
  if (length(zz)==0) {
    print(paste("Missing", z, "Mindprint score"))
  }
}

# Identify students who are missing ACT  scores
for (i in 1:length(MindprintDF$customer_id)) {
  # we have their mindprint scores
  z <- MindprintDF$customer_id[i]
  zz <- which(ACTscaledscores$customer_id==z)
  # but not their ACT scores
  if (length(zz)==0) {
    print(paste("Missing", z, "ACT score"))
  }
}

```

## LOAD SAT DATA
```{r setup, include=FALSE, warning=FALSE}
# Load multiple excel sheets at once

# get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/SAT_Scores_112718.xlsx")

# load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/SAT_Scores_112718.xlsx", sheet = sheet)
)

# prepare names
names(lst) <- sheets

# turn each sheet into DF
list2env(lst, envir = .GlobalEnv)

# combine all SAT scores
SATscaledscores <- rbind(Manjri, Maureen, APlus, Paidosh, SmartyPrep)

## Merge with Mindprint DF
MindprintDF <- merge(Mindprint, SATscaledscores, by = "customer_id")

# save to computer
write.csv(MindprintDF, "Mindprint_SATScores.csv", row.names=TRUE) #save to computer
```

