---
title: "Mindprint - Math"
author: "Felicia Zhang"
date: '2018-07-25'
output: pdf_document
toc: yes
toc_depth: 2
fontsize: 12pt
fig_height: 5
fig_width: 7
---

```{r setup, include=FALSE, warning=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)
library(readxl)    
library(extrafont)

## 1. Load ACT/SAT data

#LOAD MULTIPLE EXCEL SHEETS INTO SEPARATE DFS

#get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/Math.xlsx")

#load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/Math.xlsx", sheet = sheet)
)

#prepare names
names(lst) <- sheets

#turn it into DF
list2env(lst, envir = .GlobalEnv)

#difference between 70C, 72C, Combo v2.4: three different tests based on where we had sufficient student data, noting the one called the Combo is a mixture of SAT and ACT questions.

#0 = incorrect, 1 = correct, 2 = skip

## 2. Load mindprint data
mindprintdata <- read.csv("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/mindprint_data.csv", header=T)
```

```{r, echo=FALSE, warning=FALSE, include=FALSE}
## SET UP DF
names(`70C`)[2:61] = 1:60
names(`72C`)[2:61] = 1:60

# Mindprint subjects
subs <- unique(mindprintdata$student_id)

# duplicates = subID 441, 8826, 4573, 

# Find matching subjects in 70C
z <- which(`70C`$Question=="student_id")
zz <- length(`70C`$Question)
foo <- `70C`[(z+1):zz,]
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
colnames(foo)[1] <- "student_id"

foofinal1 <- merge(mindprintdata, foo)

# Find matching subjects in 72C
z <- which(`72C`$Question=="student_id")
zz <- length(`72C`$Question)
foo <- `72C`[(z+1):zz,]
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
colnames(foo)[1] <- "student_id"

foofinal2 <- merge(mindprintdata, foo)

finalDF <- rbind(foofinal1,foofinal2)

# calculate ACT math score (total number of questions = 60)
finalDF$ACTmathraw <- rowSums(finalDF[43:102])
finalDF$ACTmathscore <- finalDF$ACTmathraw / 60

# remove missing data
finalDF2 <- na.omit(finalDF)
```

\newpage

# ACT Math (n = 61)
## Overall score 
### Visual motor speed 
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=SM_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed score for visual motor speed", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)
  
cor.test(finalDF2$SM_Sz, finalDF2$ACTmathscore, method="pearson")
```
\newpage

### Verbal memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=VMEM_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$VMEM_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Verbal memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=VMEM_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$VMEM_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Flexible thinking accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=ABF_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for flexible thinking", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$ABF_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Flexible thinking speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=ABF_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for flexible thinking", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$ABF_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Verbal reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=LAN_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$LAN_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Verbal reasoning speed 
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=LAN_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$LAN_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Abstract reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=NVR_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for abstract reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$NVR_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Abstract reasoning speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=NVR_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for abstract reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$NVR_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Working memory accuracy  (p = 0.07)
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=WM_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for working memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$WM_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Working memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=WM_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for working memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$WM_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Working memory efficiency (p < 0.05)
##### Average of normed accuracy and speed scores for working memory.
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=WM_EFFICIENCY,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Average of normed accuracy and speed scores for working memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$WM_EFFICIENCY, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Attention accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=ATT_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for attention", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$ATT_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Attention speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=ATT_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for attention", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$ATT_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Visual memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=SMEM_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for visual memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$SMEM_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Visual memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=SMEM_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for visual memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$SMEM_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

### Spatial perception accuracy (p < 0.01)
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=SPA_Az,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for spatial perception", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$SPA_Az, finalDF2$ACTmathscore, method="pearson")  
```
\newpage

### Spatial perception speed
```{r, echo=FALSE, warning=FALSE}

ggplot(finalDF2,aes(x=SPA_Sz,y=ACTmathscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for spatial perception", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(finalDF2$SPA_Sz, finalDF2$ACTmathscore, method="pearson")    
```
\newpage

```{r, echo=FALSE, warning=FALSE, include=FALSE}
#set up subsection DF
foo <- `70C`[1:4,]
subsection <- t(foo)
subsection <- data.frame(subsection)
subsection <- subsection[-1, ] 

colnames(subsection)[1] <- "test"
colnames(subsection)[2] <- "question"
colnames(subsection)[3] <- "section"
colnames(subsection)[4] <- "subsection"

EA <- subset(subsection, subsection=="EA")
GT <- subset(subsection, subsection=="GT")
AG <- subset(subsection, subsection=="AG")

EAnum <- unique(EA$question)
EAnum <- as.numeric(EAnum)
GTnum <- unique(GT$question)
GTnum <- as.numeric(GTnum)
AGnum <- unique(AG$question)
AGnum <- as.numeric(AGnum)

#all questions
questions <- finalDF2[,43:102]

#AG DF
AG_DF <- questions[,AGnum]
AG_DF$AGraw <- rowSums(AG_DF)
AG_DF$AGscore <- AG_DF$AGraw / length(AGnum)
AG_DF <- cbind(finalDF2[,1:42],AG_DF)

#EA DF
EA_DF <- questions[,EAnum]
EA_DF$EAraw <- rowSums(EA_DF)
EA_DF$EAscore <- EA_DF$EAraw / length(EAnum)
EA_DF <- cbind(finalDF2[,1:42],EA_DF)

#GT DF
GT_DF <- questions[,GTnum]
GT_DF$GTraw <- rowSums(GT_DF)
GT_DF$GTscore <- GT_DF$GTraw / length(GTnum)
GT_DF <- cbind(finalDF2[,1:42],GT_DF)
```

## EA/ Pre-Algebra/Elementary Algebra Subsection
### Visual motor speed  
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=SM_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed score for visual motor speed", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)
  
cor.test(EA_DF$SM_Sz, EA_DF$EAscore, method="pearson")
```
\newpage

### Verbal memory accuracy 
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=VMEM_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$VMEM_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Verbal memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=VMEM_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$VMEM_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Flexible thinking accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=ABF_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for flexible thinking", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$ABF_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Flexible thinking speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=ABF_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for flexible thinking", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$ABF_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Verbal reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=LAN_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$LAN_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Verbal reasoning speed 
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=LAN_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$LAN_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Abstract reasoning accuracy (p = 0.08)
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=NVR_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for abstract reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$NVR_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Abstract reasoning speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=NVR_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for abstract reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$NVR_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Working memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=WM_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for working memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$WM_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Working memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=WM_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for working memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$WM_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Working memory efficiency 
##### Average of normed accuracy and speed scores for working memory.
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=WM_EFFICIENCY,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Average of normed accuracy and speed scores for working memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$WM_EFFICIENCY, EA_DF$EAscore, method="pearson")    
```
\newpage

### Attention accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=ATT_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for attention", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$ATT_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Attention speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=ATT_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for attention", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$ATT_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Visual memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=SMEM_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for visual memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$SMEM_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Visual memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=SMEM_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for visual memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$SMEM_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

### Spatial perception accuracy (p < 0.001)
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=SPA_Az,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for spatial perception", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$SPA_Az, EA_DF$EAscore, method="pearson")  
```
\newpage

### Spatial perception speed
```{r, echo=FALSE, warning=FALSE}

ggplot(EA_DF,aes(x=SPA_Sz,y=EAscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for spatial perception", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(EA_DF$SPA_Sz, EA_DF$EAscore, method="pearson")    
```
\newpage

## GT/ Plane Geometry/Trigonometry Subsection
### Visual motor speed  
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=SM_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed score for visual motor speed", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)
  
cor.test(GT_DF$SM_Sz, GT_DF$GTscore, method="pearson")
```
\newpage

### Verbal memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=VMEM_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$VMEM_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Verbal memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=VMEM_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$VMEM_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Flexible thinking accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=ABF_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for flexible thinking", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$ABF_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Flexible thinking speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=ABF_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for flexible thinking", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$ABF_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Verbal reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=LAN_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$LAN_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Verbal reasoning speed 
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=LAN_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$LAN_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Abstract reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=NVR_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for abstract reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$NVR_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Abstract reasoning speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=NVR_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for abstract reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$NVR_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Working memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=WM_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for working memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$WM_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Working memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=WM_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for working memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$WM_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Working memory efficiency (p = 0.07)
##### Average of normed accuracy and speed scores for working memory.
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=WM_EFFICIENCY,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Average of normed accuracy and speed scores for working memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$WM_EFFICIENCY, GT_DF$GTscore, method="pearson")    
```
\newpage

### Attention accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=ATT_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for attention", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$ATT_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Attention speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=ATT_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for attention", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$ATT_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Visual memory accuracy 
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=SMEM_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for visual memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$SMEM_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Visual memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=SMEM_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for visual memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$SMEM_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

### Spatial perception accuracy (p < 0.05)
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=SPA_Az,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for spatial perception", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$SPA_Az, GT_DF$GTscore, method="pearson")  
```
\newpage

### Spatial perception speed
```{r, echo=FALSE, warning=FALSE}

ggplot(GT_DF,aes(x=SPA_Sz,y=GTscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for spatial perception", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(GT_DF$SPA_Sz, GT_DF$GTscore, method="pearson")    
```
\newpage

## AG/ Intermediate Algebra/Coordinate Geometry Subsection
### Visual motor speed  
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=SM_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed score for visual motor speed", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)
  
cor.test(AG_DF$SM_Sz, AG_DF$AGscore, method="pearson")
```
\newpage

### Verbal memory accuracy 
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=VMEM_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$VMEM_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Verbal memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=VMEM_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$VMEM_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Flexible thinking accuracy 
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=ABF_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for flexible thinking", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$ABF_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Flexible thinking speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=ABF_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for flexible thinking", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$ABF_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Verbal reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=LAN_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for verbal reasoning", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$LAN_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Verbal reasoning speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=LAN_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for verbal reasoning", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$LAN_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Abstract reasoning accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=NVR_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for abstract reasoning", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$NVR_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Abstract reasoning speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=NVR_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for abstract reasoning", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$NVR_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Working memory accuracy (p < 0.05)
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=WM_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for working memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$WM_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Working memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=WM_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for working memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$WM_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Working memory efficiency (p < 0.05)
##### Average of normed accuracy and speed scores for working memory.
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=WM_EFFICIENCY,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Average of normed accuracy and speed scores for working memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$WM_EFFICIENCY, AG_DF$AGscore, method="pearson")    
```
\newpage

### Attention accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=ATT_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for attention", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$ATT_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Attention speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=ATT_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for attention", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$ATT_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Visual memory accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=SMEM_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for visual memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$SMEM_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Visual memory speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=SMEM_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for visual memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$SMEM_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

### Spatial perception accuracy
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=SPA_Az,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed accuracy score for spatial perception", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$SPA_Az, AG_DF$AGscore, method="pearson")  
```
\newpage

### Spatial perception speed
```{r, echo=FALSE, warning=FALSE}

ggplot(AG_DF,aes(x=SPA_Sz,y=AGscore))+
  geom_point(size=3)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Normed speed score for spatial perception", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  stat_smooth(method=lm, se=FALSE)

cor.test(AG_DF$SPA_Sz, AG_DF$AGscore, method="pearson")    
```
\newpage

## Summary

1. Spatial perception accuracy predicts overall math score, pre-algebra, trig 
2. WM efficiency predicts overall math score, trig (almost), intermediate algebra/geometry
3. WM accuracy predicts intermediate algebra/geometry
4. Abstract reasoning accuracy predicts pre-algebra

