---
title: "Mindprint - Math - 7 bins"
author: "Felicia Zhang"
date: '2018-08-05'
output: pdf_document
toc: yes
toc_depth: 2
fontsize: 12pt
fig_height: 5
fig_width: 7
---

```{r setup, include=FALSE, warning=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(broom)
library(tidyr)
library(wesanderson)
library(readxl)    
library(extrafont)

## 1. Load ACT/SAT data

#LOAD MULTIPLE EXCEL SHEETS INTO SEPARATE DFS

#get names of sheets
sheets <- readxl::excel_sheets("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/Math.xlsx")

#load in excel data as 1 big file
lst <- lapply(sheets, function(sheet) 
  readxl::read_excel("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/Math.xlsx", sheet = sheet)
)

#prepare names
names(lst) <- sheets

#turn it into DF
list2env(lst, envir = .GlobalEnv)

#difference between 70C, 72C, Combo v2.4: three different tests based on where we had sufficient student data, noting the one called the Combo is a mixture of SAT and ACT questions.

#0 = incorrect, 1 = correct, 2 = skip

## 2. Load mindprint data
mindprintdata <- read.csv("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/mindprint_data.csv", header=T)
```

```{r, echo=FALSE, warning=FALSE, include=FALSE}
## SET UP DF
names(`70C`)[2:61] = 1:60
names(`72C`)[2:61] = 1:60

# Mindprint subjects
subs <- unique(mindprintdata$student_id)

# duplicates = subID 441, 8826, 4573, 

# Find matching subjects in 70C
z <- which(`70C`$Question=="student_id")
zz <- length(`70C`$Question)
foo <- `70C`[(z+1):zz,]
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
colnames(foo)[1] <- "student_id"

foofinal1 <- merge(mindprintdata, foo)

# Find matching subjects in 72C
z <- which(`72C`$Question=="student_id")
zz <- length(`72C`$Question)
foo <- `72C`[(z+1):zz,]
foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
colnames(foo)[1] <- "student_id"

foofinal2 <- merge(mindprintdata, foo)

finalDF <- rbind(foofinal1,foofinal2)

# calculate ACT math score (total number of questions = 60)
finalDF$ACTmathraw <- rowSums(finalDF[43:102])
finalDF$ACTmathscore <- finalDF$ACTmathraw / 60

# remove missing data
finalDF2 <- na.omit(finalDF)
```

\newpage

# ACT Math (n = 61) | 7 bins
## Overall score 
### Visual motor
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, SM_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SM_SCORE=="low_weakness"] <- 1
goo$bin[goo$SM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SM_SCORE=="low_expected"] <- 3
goo$bin[goo$SM_SCORE=="medium_expected"] <- 4
goo$bin[goo$SM_SCORE=="high_expected"] <- 5
goo$bin[goo$SM_SCORE=="medium_strength"] <- 6
goo$bin[goo$SM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual motor", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Flexible thinking
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, ABF_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ABF_SCORE=="low_weakness"] <- 1
goo$bin[goo$ABF_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ABF_SCORE=="low_expected"] <- 3
goo$bin[goo$ABF_SCORE=="medium_expected"] <- 4
goo$bin[goo$ABF_SCORE=="high_expected"] <- 5
goo$bin[goo$ABF_SCORE=="medium_strength"] <- 6
goo$bin[goo$ABF_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Flexible thinking", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, LAN_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$LAN_SCORE=="low_weakness"] <- 1
goo$bin[goo$LAN_SCORE=="medium_weakness"] <- 2
goo$bin[goo$LAN_SCORE=="low_expected"] <- 3
goo$bin[goo$LAN_SCORE=="medium_expected"] <- 4
goo$bin[goo$LAN_SCORE=="high_expected"] <- 5
goo$bin[goo$LAN_SCORE=="medium_strength"] <- 6
goo$bin[goo$LAN_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Abstract reasoning
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, NVR_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$NVR_SCORE=="low_weakness"] <- 1
goo$bin[goo$NVR_SCORE=="medium_weakness"] <- 2
goo$bin[goo$NVR_SCORE=="low_expected"] <- 3
goo$bin[goo$NVR_SCORE=="medium_expected"] <- 4
goo$bin[goo$NVR_SCORE=="high_expected"] <- 5
goo$bin[goo$NVR_SCORE=="medium_strength"] <- 6
goo$bin[goo$NVR_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Abstract reasoning", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Working memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, WM_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$WM_SCORE=="low_weakness"] <- 1
goo$bin[goo$WM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$WM_SCORE=="low_expected"] <- 3
goo$bin[goo$WM_SCORE=="medium_expected"] <- 4
goo$bin[goo$WM_SCORE=="high_expected"] <- 5
goo$bin[goo$WM_SCORE=="medium_strength"] <- 6
goo$bin[goo$WM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Working memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Attention
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, ATT_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ATT_SCORE=="low_weakness"] <- 1
goo$bin[goo$ATT_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ATT_SCORE=="low_expected"] <- 3
goo$bin[goo$ATT_SCORE=="medium_expected"] <- 4
goo$bin[goo$ATT_SCORE=="high_expected"] <- 5
goo$bin[goo$ATT_SCORE=="medium_strength"] <- 6
goo$bin[goo$ATT_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Attention", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Visual memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual memory", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Spatial perception (p = 0.004, r = 0.95)
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(finalDF2, SPA_SCORE) %>%
  summarise(
    avgMath = mean(ACTmathscore, na.rm = TRUE),
    seMAth=sd(ACTmathscore, na.rm = TRUE)/sqrt(length(ACTmathscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SPA_SCORE=="low_weakness"] <- 1
goo$bin[goo$SPA_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SPA_SCORE=="low_expected"] <- 3
goo$bin[goo$SPA_SCORE=="medium_expected"] <- 4
goo$bin[goo$SPA_SCORE=="high_expected"] <- 5
goo$bin[goo$SPA_SCORE=="medium_strength"] <- 6
goo$bin[goo$SPA_SCORE=="high_strength"] <- 7

goo <- subset(goo, bin > 0)

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Spatial perception", y = "ACT math score (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson") 
```
\newpage

```{r, echo=FALSE, warning=FALSE, include=FALSE}
# figure out which subsection each question corresponded to
foo <- `70C`[c(1,2,3,4,20),]
subsection <- t(foo)
subsection <- data.frame(subsection)
subsection <- subsection[-1, ] 

colnames(subsection)[1] <- "test"
colnames(subsection)[2] <- "question"
colnames(subsection)[3] <- "section"
colnames(subsection)[4] <- "subsection"
colnames(subsection)[5] <- "difficulty"

EA <- subset(subsection, subsection=="EA")
GT <- subset(subsection, subsection=="GT")
AG <- subset(subsection, subsection=="AG")

EAnum <- unique(EA$question)
EAnum <- as.numeric(EAnum)
GTnum <- unique(GT$question)
GTnum <- as.numeric(GTnum)
AGnum <- unique(AG$question)
AGnum <- as.numeric(AGnum)

#all questions
questions <- finalDF2[,43:102]

#AG DF
AG_DF <- questions[,AGnum]
AG_DF$AGraw <- rowSums(AG_DF)
AG_DF$AGscore <- AG_DF$AGraw / length(AGnum)
AG_DF <- cbind(finalDF2[,1:42],AG_DF)

#EA DF
EA_DF <- questions[,EAnum]
EA_DF$EAraw <- rowSums(EA_DF)
EA_DF$EAscore <- EA_DF$EAraw / length(EAnum)
EA_DF <- cbind(finalDF2[,1:42],EA_DF)

#GT DF
GT_DF <- questions[,GTnum]
GT_DF$GTraw <- rowSums(GT_DF)
GT_DF$GTscore <- GT_DF$GTraw / length(GTnum)
GT_DF <- cbind(finalDF2[,1:42],GT_DF)
```

## EA/ Pre-Algebra/Elementary Algebra Subsection

### Visual motor
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF,SM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SM_SCORE=="low_weakness"] <- 1
goo$bin[goo$SM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SM_SCORE=="low_expected"] <- 3
goo$bin[goo$SM_SCORE=="medium_expected"] <- 4
goo$bin[goo$SM_SCORE=="high_expected"] <- 5
goo$bin[goo$SM_SCORE=="medium_strength"] <- 6
goo$bin[goo$SM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual motor", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Flexible thinking
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, ABF_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ABF_SCORE=="low_weakness"] <- 1
goo$bin[goo$ABF_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ABF_SCORE=="low_expected"] <- 3
goo$bin[goo$ABF_SCORE=="medium_expected"] <- 4
goo$bin[goo$ABF_SCORE=="high_expected"] <- 5
goo$bin[goo$ABF_SCORE=="medium_strength"] <- 6
goo$bin[goo$ABF_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Flexible thinking", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, LAN_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$LAN_SCORE=="low_weakness"] <- 1
goo$bin[goo$LAN_SCORE=="medium_weakness"] <- 2
goo$bin[goo$LAN_SCORE=="low_expected"] <- 3
goo$bin[goo$LAN_SCORE=="medium_expected"] <- 4
goo$bin[goo$LAN_SCORE=="high_expected"] <- 5
goo$bin[goo$LAN_SCORE=="medium_strength"] <- 6
goo$bin[goo$LAN_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Abstract reasoning
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, NVR_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$NVR_SCORE=="low_weakness"] <- 1
goo$bin[goo$NVR_SCORE=="medium_weakness"] <- 2
goo$bin[goo$NVR_SCORE=="low_expected"] <- 3
goo$bin[goo$NVR_SCORE=="medium_expected"] <- 4
goo$bin[goo$NVR_SCORE=="high_expected"] <- 5
goo$bin[goo$NVR_SCORE=="medium_strength"] <- 6
goo$bin[goo$NVR_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Abstract reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Working memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, WM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$WM_SCORE=="low_weakness"] <- 1
goo$bin[goo$WM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$WM_SCORE=="low_expected"] <- 3
goo$bin[goo$WM_SCORE=="medium_expected"] <- 4
goo$bin[goo$WM_SCORE=="high_expected"] <- 5
goo$bin[goo$WM_SCORE=="medium_strength"] <- 6
goo$bin[goo$WM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Working memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Attention
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, ATT_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ATT_SCORE=="low_weakness"] <- 1
goo$bin[goo$ATT_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ATT_SCORE=="low_expected"] <- 3
goo$bin[goo$ATT_SCORE=="medium_expected"] <- 4
goo$bin[goo$ATT_SCORE=="high_expected"] <- 5
goo$bin[goo$ATT_SCORE=="medium_strength"] <- 6
goo$bin[goo$ATT_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Attention", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Visual memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Spatial perception (p = 0.001, r = 0.97)
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF,SPA_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SPA_SCORE=="low_weakness"] <- 1
goo$bin[goo$SPA_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SPA_SCORE=="low_expected"] <- 3
goo$bin[goo$SPA_SCORE=="medium_expected"] <- 4
goo$bin[goo$SPA_SCORE=="high_expected"] <- 5
goo$bin[goo$SPA_SCORE=="medium_strength"] <- 6
goo$bin[goo$SPA_SCORE=="high_strength"] <- 7

goo <- subset(goo, bin > 0)

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Spatial perception", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson") 
```
\newpage

## GT/ Plane Geometry/Trigonometry Subsection

### Visual motor
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF,SM_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SM_SCORE=="low_weakness"] <- 1
goo$bin[goo$SM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SM_SCORE=="low_expected"] <- 3
goo$bin[goo$SM_SCORE=="medium_expected"] <- 4
goo$bin[goo$SM_SCORE=="high_expected"] <- 5
goo$bin[goo$SM_SCORE=="medium_strength"] <- 6
goo$bin[goo$SM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual motor", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Flexible thinking
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF, ABF_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ABF_SCORE=="low_weakness"] <- 1
goo$bin[goo$ABF_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ABF_SCORE=="low_expected"] <- 3
goo$bin[goo$ABF_SCORE=="medium_expected"] <- 4
goo$bin[goo$ABF_SCORE=="high_expected"] <- 5
goo$bin[goo$ABF_SCORE=="medium_strength"] <- 6
goo$bin[goo$ABF_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Flexible thinking", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF, LAN_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$LAN_SCORE=="low_weakness"] <- 1
goo$bin[goo$LAN_SCORE=="medium_weakness"] <- 2
goo$bin[goo$LAN_SCORE=="low_expected"] <- 3
goo$bin[goo$LAN_SCORE=="medium_expected"] <- 4
goo$bin[goo$LAN_SCORE=="high_expected"] <- 5
goo$bin[goo$LAN_SCORE=="medium_strength"] <- 6
goo$bin[goo$LAN_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Abstract reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF,NVR_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$NVR_SCORE=="low_weakness"] <- 1
goo$bin[goo$NVR_SCORE=="medium_weakness"] <- 2
goo$bin[goo$NVR_SCORE=="low_expected"] <- 3
goo$bin[goo$NVR_SCORE=="medium_expected"] <- 4
goo$bin[goo$NVR_SCORE=="high_expected"] <- 5
goo$bin[goo$NVR_SCORE=="medium_strength"] <- 6
goo$bin[goo$NVR_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Abstract reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
  
```
\newpage

### Working memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, WM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$WM_SCORE=="low_weakness"] <- 1
goo$bin[goo$WM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$WM_SCORE=="low_expected"] <- 3
goo$bin[goo$WM_SCORE=="medium_expected"] <- 4
goo$bin[goo$WM_SCORE=="high_expected"] <- 5
goo$bin[goo$WM_SCORE=="medium_strength"] <- 6
goo$bin[goo$WM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Working memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Attention
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, ATT_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ATT_SCORE=="low_weakness"] <- 1
goo$bin[goo$ATT_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ATT_SCORE=="low_expected"] <- 3
goo$bin[goo$ATT_SCORE=="medium_expected"] <- 4
goo$bin[goo$ATT_SCORE=="high_expected"] <- 5
goo$bin[goo$ATT_SCORE=="medium_strength"] <- 6
goo$bin[goo$ATT_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Attention", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Visual memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(EA_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(EAscore, na.rm = TRUE),
    seMAth=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual memory", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Spatial perception (p = 0.009, r = 0.92)
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(GT_DF,SPA_SCORE) %>%
  summarise(
    avgMath = mean(GTscore, na.rm = TRUE),
    seMAth=sd(GTscore, na.rm = TRUE)/sqrt(length(GTscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SPA_SCORE=="low_weakness"] <- 1
goo$bin[goo$SPA_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SPA_SCORE=="low_expected"] <- 3
goo$bin[goo$SPA_SCORE=="medium_expected"] <- 4
goo$bin[goo$SPA_SCORE=="high_expected"] <- 5
goo$bin[goo$SPA_SCORE=="medium_strength"] <- 6
goo$bin[goo$SPA_SCORE=="high_strength"] <- 7

goo <- subset(goo, bin > 0)

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Spatial perception", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson") 
```
\newpage

## AG/ Intermediate Algebra/Coordinate Geometry Subsection
### Visual motor
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF,SM_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SM_SCORE=="low_weakness"] <- 1
goo$bin[goo$SM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SM_SCORE=="low_expected"] <- 3
goo$bin[goo$SM_SCORE=="medium_expected"] <- 4
goo$bin[goo$SM_SCORE=="high_expected"] <- 5
goo$bin[goo$SM_SCORE=="medium_strength"] <- 6
goo$bin[goo$SM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual motor", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal memory", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Flexible thinking
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF, ABF_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ABF_SCORE=="low_weakness"] <- 1
goo$bin[goo$ABF_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ABF_SCORE=="low_expected"] <- 3
goo$bin[goo$ABF_SCORE=="medium_expected"] <- 4
goo$bin[goo$ABF_SCORE=="high_expected"] <- 5
goo$bin[goo$ABF_SCORE=="medium_strength"] <- 6
goo$bin[goo$ABF_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Flexible thinking", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Verbal reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF, LAN_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$LAN_SCORE=="low_weakness"] <- 1
goo$bin[goo$LAN_SCORE=="medium_weakness"] <- 2
goo$bin[goo$LAN_SCORE=="low_expected"] <- 3
goo$bin[goo$LAN_SCORE=="medium_expected"] <- 4
goo$bin[goo$LAN_SCORE=="high_expected"] <- 5
goo$bin[goo$LAN_SCORE=="medium_strength"] <- 6
goo$bin[goo$LAN_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Verbal reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Abstract reasoning 
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF,NVR_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$NVR_SCORE=="low_weakness"] <- 1
goo$bin[goo$NVR_SCORE=="medium_weakness"] <- 2
goo$bin[goo$NVR_SCORE=="low_expected"] <- 3
goo$bin[goo$NVR_SCORE=="medium_expected"] <- 4
goo$bin[goo$NVR_SCORE=="high_expected"] <- 5
goo$bin[goo$NVR_SCORE=="medium_strength"] <- 6
goo$bin[goo$NVR_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Abstract reasoning", y = "Plane Geometry/Trigonometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
  
```
\newpage

### Working memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF,WM_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$WM_SCORE=="low_weakness"] <- 1
goo$bin[goo$WM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$WM_SCORE=="low_expected"] <- 3
goo$bin[goo$WM_SCORE=="medium_expected"] <- 4
goo$bin[goo$WM_SCORE=="high_expected"] <- 5
goo$bin[goo$WM_SCORE=="medium_strength"] <- 6
goo$bin[goo$WM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Working memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Attention
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF, ATT_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$ATT_SCORE=="low_weakness"] <- 1
goo$bin[goo$ATT_SCORE=="medium_weakness"] <- 2
goo$bin[goo$ATT_SCORE=="low_expected"] <- 3
goo$bin[goo$ATT_SCORE=="medium_expected"] <- 4
goo$bin[goo$ATT_SCORE=="high_expected"] <- 5
goo$bin[goo$ATT_SCORE=="medium_strength"] <- 6
goo$bin[goo$ATT_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Attention", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Visual memory
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF, VMEM_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$VMEM_SCORE=="low_weakness"] <- 1
goo$bin[goo$VMEM_SCORE=="medium_weakness"] <- 2
goo$bin[goo$VMEM_SCORE=="low_expected"] <- 3
goo$bin[goo$VMEM_SCORE=="medium_expected"] <- 4
goo$bin[goo$VMEM_SCORE=="high_expected"] <- 5
goo$bin[goo$VMEM_SCORE=="medium_strength"] <- 6
goo$bin[goo$VMEM_SCORE=="high_strength"] <- 7

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Visual memory", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson")
```
\newpage

### Spatial perception (p = 0.01, r = 0.92)
```{r, echo=FALSE, warning=FALSE}
goo <- group_by(AG_DF,SPA_SCORE) %>%
  summarise(
    avgMath = mean(AGscore, na.rm = TRUE),
    seMAth=sd(AGscore, na.rm = TRUE)/sqrt(length(AGscore)),
    num = length(unique(student_id))
  )

goo$bin <- 0
goo$bin[goo$SPA_SCORE=="low_weakness"] <- 1
goo$bin[goo$SPA_SCORE=="medium_weakness"] <- 2
goo$bin[goo$SPA_SCORE=="low_expected"] <- 3
goo$bin[goo$SPA_SCORE=="medium_expected"] <- 4
goo$bin[goo$SPA_SCORE=="high_expected"] <- 5
goo$bin[goo$SPA_SCORE=="medium_strength"] <- 6
goo$bin[goo$SPA_SCORE=="high_strength"] <- 7

goo <- subset(goo, bin > 0)

limits <- aes(ymax = avgMath + seMAth, ymin=avgMath - seMAth)

ggplot(goo,aes(x=factor(bin),y=avgMath))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Spatial perception", y = "Intermediate Algebra/Coordinate Geometry (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"), axis.text.x = element_text(angle=60, hjust=1))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))

cor.test(goo$bin, goo$avgMath, method="pearson") 
```
\newpage

```{r, echo=FALSE, warning=FALSE, include=FALSE}
#prepare data for level of difficulty analyses

foo <- `70C`[c(1,2,3,4,20),]
subsection <- t(foo)
subsection <- data.frame(subsection)
subsection <- subsection[-1, ] 

colnames(subsection)[1] <- "test"
colnames(subsection)[2] <- "question"
colnames(subsection)[3] <- "section"
colnames(subsection)[4] <- "subsection"
colnames(subsection)[5] <- "difficulty"

questions2 <- t(questions)
subsection <- cbind(subsection, questions2)

write.csv(subsection, "mindprintdifficuty.csv", row.names=TRUE) #save to computer

## Load mindprint difficulty data
q.difficulty <- read.csv("~/Documents/Felicia Zhang/Felicia/Princeton/ConsultingClub/Mindprint/mindprintdifficuty.csv", header=T)

finalDF3 <- cbind(finalDF2, q.difficulty)
```

## Appleseed Suggested Analyses
### EA - abstract reasoning model
```{r, echo=FALSE, warning=FALSE}
EA_AbsRea <- EA_DF
EA_AbsRea$bin <- 0
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="low_weakness"] <- 1
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="medium_weakness"] <- 2
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="low_expected"] <- 3
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="medium_expected"] <- 4
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="high_expected"] <- 5
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="medium_strength"] <- 6
EA_AbsRea$bin[EA_AbsRea$NVR_SCORE=="high_strength"] <- 7

EA_model <- lm(EAscore ~ bin, data=EA_AbsRea)  # accuracy
summary(EA_model)

goo <- group_by(EA_AbsRea,NVR_SCORE,bin) %>%
  summarise(
    avgEA = mean(EAscore, na.rm = TRUE),
    seEA=sd(EAscore, na.rm = TRUE)/sqrt(length(EAscore)),
    num = length(unique(student_id))
  )

ggplot(goo,aes(x=factor(bin),y=avgEA))+
  geom_point(aes(size = num))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Abstract reasoning", y = "Pre-Algebra/Elementary Algebra (% correct)")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=14))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text=element_text(family="Times"))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))+
  scale_x_discrete(breaks=c("1","2","3","4","5","6","7"),labels=c("low weakness", "medium weakness","low expected","medium expected","high expected","medium strength","high strength"))
  
cor.test(goo$bin, goo$avgEA, method="pearson")  
```
Elementary algebra is not predicted by abstract reasoning accuracy (p=0.645).

### EA - abstract reasoning broken down by difficulty of questions

Level 1 EA
```{r, echo=FALSE, warning=FALSE}
finalDF3$bin_absrea <- 0
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="low_weakness"] <- 1
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="medium_weakness"] <- 2
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="low_expected"] <- 3
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="medium_expected"] <- 4
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="high_expected"] <- 5
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="medium_strength"] <- 6
finalDF3$bin_absrea[finalDF3$NVR_SCORE=="high_strength"] <- 7

#level 1 
EA1 <- lm(EA1 ~ bin_absrea, data=finalDF3)  # accuracy
summary(EA1)
```

Level 2 EA
```{r, echo=FALSE, warning=FALSE}
#level 2
EA2 <- lm(EA2 ~ bin_absrea, data=finalDF3)  # accuracy
summary(EA2)
```

Level 3 EA
```{r, echo=FALSE, warning=FALSE}
#level 3
EA3 <- lm(EA3 ~ bin_absrea, data=finalDF3)  # accuracy
summary(EA3)
```

Level 4 EA
```{r, echo=FALSE, warning=FALSE}
#level 4
EA4 <- lm(EA4 ~ bin_absrea, data=finalDF3)  # accuracy
summary(EA4)
```

Level 5 EA
```{r, echo=FALSE, warning=FALSE}
#level 5
EA5 <- lm(EA5 ~ bin_absrea, data=finalDF3)  # accuracy
summary(EA5)
```
Elementary algebra is not predicted by abstract reasoning accuracy.

\newpage

### GT - abstract reasoning & spatial perception
```{r, echo=FALSE, warning=FALSE}
GT_DF2 <- GT_DF
GT_DF2$bin_absrea <- 0
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="low_weakness"] <- 1
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="medium_weakness"] <- 2
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="low_expected"] <- 3
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="medium_expected"] <- 4
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="high_expected"] <- 5
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="medium_strength"] <- 6
GT_DF2$bin_absrea[GT_DF2$NVR_SCORE=="high_strength"] <- 7

GT_DF2$bin_spaper <- 0
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="low_weakness"] <- 1
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="medium_weakness"] <- 2
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="low_expected"] <- 3
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="medium_expected"] <- 4
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="high_expected"] <- 5
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="medium_strength"] <- 6
GT_DF2$bin_spaper[GT_DF2$SPA_SCORE=="high_strength"] <- 7

GT_model <- lm(GTscore ~ bin_absrea + bin_spaper, data=GT_DF2)  

summary(GT_model)
```
Plane geometry/trigonometry is predicted by spatial perception accuracy (p=0.042).

\newpage

### GT - abstract reasoning & spatial perception broken down by difficulty of questions

Level 1 GT
```{r, echo=FALSE, warning=FALSE}
finalDF3$bin_spaper <- 0
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="low_weakness"] <- 1
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="medium_weakness"] <- 2
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="low_expected"] <- 3
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="medium_expected"] <- 4
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="high_expected"] <- 5
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="medium_strength"] <- 6
finalDF3$bin_spaper[finalDF3$SPA_SCORE=="high_strength"] <- 7

#level 1 
GT1 <- lm(GT1 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(GT1)
```

Level 2 GT
```{r, echo=FALSE, warning=FALSE}
#level 2
GT2 <- lm(GT2 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(GT2)
```

Level 3 GT
```{r, echo=FALSE, warning=FALSE}
#level 3
GT3 <- lm(GT3 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(GT3)
```

Level 4 GT
```{r, echo=FALSE, warning=FALSE}
#level 4
GT4 <- lm(GT4 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(GT4)
```

Level 5 GT
```{r, echo=FALSE, warning=FALSE}
#level 5
GT5 <- lm(GT5 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(GT5)
```
Difficult questions level 3-5 of plane geometry/trigonometry is predicted by spatial perception accuracy.

\newpage

### AG - abstract reasoning & spatial perception
```{r, echo=FALSE, warning=FALSE}
AG_DF2 <- AG_DF
AG_DF2$bin_absrea <- 0
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="low_weakness"] <- 1
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="medium_weakness"] <- 2
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="low_expected"] <- 3
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="medium_expected"] <- 4
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="high_expected"] <- 5
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="medium_strength"] <- 6
AG_DF2$bin_absrea[AG_DF2$NVR_SCORE=="high_strength"] <- 7

AG_DF2$bin_spaper <- 0
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="low_weakness"] <- 1
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="medium_weakness"] <- 2
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="low_expected"] <- 3
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="medium_expected"] <- 4
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="high_expected"] <- 5
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="medium_strength"] <- 6
AG_DF2$bin_spaper[AG_DF2$SPA_SCORE=="high_strength"] <- 7

AG_model <- lm(AGscore ~ bin_absrea + bin_spaper, data=AG_DF2)  

summary(AG_model)

```
Algebra/coordinate geometry is not predicted by abstract reasoning or spatial perception.

\newpage
### AG - abstract reasoning & spatial perception broken down by difficulty of questions

Level 1 AG
```{r, echo=FALSE, warning=FALSE}
#level 1 
AG1 <- lm(AG1 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(AG1)
```

Level 2 AG
```{r, echo=FALSE, warning=FALSE}
#level 2
AG2 <- lm(AG2 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(AG2)
```

Level 3 AG
```{r, echo=FALSE, warning=FALSE}
#level 3
AG3 <- lm(AG3 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(AG3)
```

Level 4 AG
```{r, echo=FALSE, warning=FALSE}
#level 4
AG4 <- lm(AG4 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(AG4)
```

Level 5 AG
```{r, echo=FALSE, warning=FALSE}
#level 5
AG5 <- lm(AG5 ~ bin_absrea + bin_spaper, data=finalDF3)  # accuracy
summary(AG5)
```
Overall algebra/coordinate geometry is not predicted by abstract reasoning or spatial perception. 
But level 1 algebra/coordinate geometry is predicted by spatial perception.

\newpage

### AG - abstract reasoning & spatial perception & flexible thinking
```{r, echo=FALSE, warning=FALSE}
AG_DF2$bin_flexthin <- 0
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="low_weakness"] <- 1
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="medium_weakness"] <- 2
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="low_expected"] <- 3
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="medium_expected"] <- 4
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="high_expected"] <- 5
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="medium_strength"] <- 6
AG_DF2$bin_flexthin[AG_DF2$ABF_SCORE=="high_strength"] <- 7

AG_model2 <- lm(AGscore ~ bin_absrea + bin_spaper + bin_flexthin, data=AG_DF2)  

summary(AG_model2)
```
Algebra/coordinate geometry is not predicted by abstract reasoning, spatial perception or flexible thinking. 

\newpage

### AG - abstract reasoning & spatial perception & flexible thinking broken down by difficulty of questions

Level 1 AG
```{r, echo=FALSE, warning=FALSE}
finalDF3$bin_flexthin <- 0
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="low_weakness"] <- 1
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="medium_weakness"] <- 2
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="low_expected"] <- 3
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="medium_expected"] <- 4
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="high_expected"] <- 5
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="medium_strength"] <- 6
finalDF3$bin_flexthin[finalDF3$ABF_SCORE=="high_strength"] <- 7

#level 1 
AG1 <- lm(AG1 ~ bin_absrea + bin_spaper + bin_flexthin, data=finalDF3)  # accuracy
summary(AG1)
```

Level 2 AG
```{r, echo=FALSE, warning=FALSE}
#level 2
AG2 <- lm(AG2 ~ bin_absrea + bin_spaper + bin_flexthin, data=finalDF3)  # accuracy
summary(AG2)
```

Level 3 AG
```{r, echo=FALSE, warning=FALSE}
#level 3
AG3 <- lm(AG3 ~ bin_absrea + bin_spaper + bin_flexthin, data=finalDF3)  # accuracy
summary(AG3)
```

Level 4 AG
```{r, echo=FALSE, warning=FALSE}
#level 4
AG4 <- lm(AG4 ~ bin_absrea + bin_spaper + bin_flexthin, data=finalDF3)  # accuracy
summary(AG4)
```

Level 5 AG
```{r, echo=FALSE, warning=FALSE}
#level 5
AG5 <- lm(AG5 ~ bin_absrea + bin_spaper + bin_flexthin, data=finalDF3)  # accuracy
summary(AG5)
```
Algebra/coordinate geometry is not predicted by abstract reasoning, spatial perception or flexible thinking. But level 1 algebra/coordinate geometry is predicted by spatial perception.

\newpage

## Summary

1. Overall math score is predicted by spatial perception.

2. Elementary algebra score is predicted by spatial perception. It is not predicted by abstract reasoning even when broken down by question difficulty.

3. Plane geometry/trigonometry score is predicted by spatial perception. Specifically, level 3-5 difficulty, of plane geometry/trigonometry is predicted by spatial perception.

4. Intermediate algebra/coordinate geometry is predicted by spatial perception (univariate analysis).   
Intermediate algebra/coordinate geometry is not predicted by abstract reasoning, spatial perception or flexible thinking (multivariate analysis).  
But level 1 algebra/coordinate geometry is predicted by spatial perception.

